An open reproducible framework for the study of the iterated prisoner's dilemma

### 2016-04-01 tex/paper.tex
Removing doctest.

\begin{figure}[!hbtp]
    \begin{minted}[linenos, frame=lines]{python}
>>> import axelrod
>>> strategies = [s() for s in axelrod.demo_strategies]
>>> tournament = axelrod.Tournament(strategies)
>>> results = tournament.play()
>>> plot = axelrod.Plot(results)
>>> plot.boxplot()  # doctest:+SKIP
    \end{minted}
    \caption{A simple set of commands to create a demonstration tournament. The
        output is shown in Figure~\ref{fig:demo_tournament}.}
    \label{fig:demo_tournament_commands}
\end{figure}

@@

>>> strategies = [axelrod.Cooperator(),
...               axelrod.Defector(),
...               axelrod.ZDExtort2(),
...               axelrod.Joss(),
...               axelrod.HardTitForTat(),
...               axelrod.HardTitFor2Tats(),
...               axelrod.TitForTat(),
...               axelrod.Grudger(),
...               axelrod.TitFor2Tats(),
...               axelrod.WinStayLoseShift(),
...               axelrod.Random(),
...               axelrod.ZDGTFT2(),
...               axelrod.GTFT(),
...               axelrod.HardProber(),
...               axelrod.Prober(),
...               axelrod.Prober2(),
...               axelrod.Prober3(),
...               axelrod.Calculator(),
...               axelrod.HardGoByMajority()]
>>> tournament = axelrod.Tournament(strategies)
>>> results = tournament.play()
>>> plot = axelrod.Plot(results)
>>> plot.boxplot()  # doctest:+SKIP
    \end{minted}
    \caption{Source code for reproducing the tournament of \cite{Stewart2012}}
    \label{fig:stewart-code}
\end{figure}

>>>>

\begin{figure}[!hbtp]
    \begin{minted}[linenos, frame=lines]{python}
>>> import axelrod
>>> strategies = [s() for s in axelrod.demo_strategies]
>>> tournament = axelrod.Tournament(strategies)
>>> results = tournament.play()
>>> plot = axelrod.Plot(results)
>>> plot.boxplot()
    \end{minted}
    \caption{A simple set of commands to create a demonstration tournament. The
        output is shown in Figure~\ref{fig:demo_tournament}.}
    \label{fig:demo_tournament_commands}
\end{figure}

@@

>>> strategies = [axelrod.Cooperator(),
...               axelrod.Defector(),
...               axelrod.ZDExtort2(),
...               axelrod.Joss(),
...               axelrod.HardTitForTat(),
...               axelrod.HardTitFor2Tats(),
...               axelrod.TitForTat(),
...               axelrod.Grudger(),
...               axelrod.TitFor2Tats(),
...               axelrod.WinStayLoseShift(),
...               axelrod.Random(),
...               axelrod.ZDGTFT2(),
...               axelrod.GTFT(),
...               axelrod.HardProber(),
...               axelrod.Prober(),
...               axelrod.Prober2(),
...               axelrod.Prober3(),
...               axelrod.Calculator(),
...               axelrod.HardGoByMajority()]
>>> tournament = axelrod.Tournament(strategies)
>>> results = tournament.play()
>>> plot = axelrod.Plot(results)
>>> plot.boxplot()
    \end{minted}
    \caption{Source code for reproducing the tournament of \cite{Stewart2012}}
    \label{fig:stewart-code}
\end{figure}
